Small(er) Samples

### 2021-06-27 R/smaller_samples.Rmd
Add data and analysis for samples run 2021-06-25.

```{r}
library(tidyverse)
library(here)
library(amstools)
library(HybridGIS)

@@

df <- read_csv(here("data_analysed/carb_all_results.csv")) %>% 
  compare_consensus() %>% 
  mutate(c12ua = he12C * 1E6)
samples <- read_csv(here("data/carb_data.csv")) %>% 
  select(wheel, pos, mass, he_added)

df <- left_join(df, samples, by = c("wheel", "pos")) %>% 
  filter(wheel != "USAMS020521")
```

@@

>>>>

```{r}
library(tidyverse)
library(here)
library(amstools)
library(hgis)

@@

df <- read_csv(here("data_analysed/carb_all_results.csv")) %>% 
  compare_consensus() %>% 
  mutate(c12ua = he12C * 1E6)
samples <- read_csv(here("data/carb_data.csv")) %>% 
  select(wheel, pos, mass, he_added)
df <- left_join(df, samples, by = c("wheel", "pos")) %>% 
  filter(wheel != "USAMS020521")
```

@@

```{r}
df %>% 
  filter(wheel == "USAMS062521") %>% 
ggplot(aes(mass, c12ua, color = as.factor(rec_num))) +
  geom_point()
```
